Representing and Reasoning About Spatial Regions Defined by Context

### 2012-01-23 code/scenarios/cdsr/trunk/papers/AAAI2012/evaluation.tex
trying to sanitise images and missing bits

\from{Nick}{TODO: Perhaps list manually encoded CDSRs}

We evaluated our approach on six classrooms (two simulated and four real) and two simulated studio apartments. The simulated rooms were based on real-life counterparts. For each room we manually encoded the appropriate CDSRs that could be represented by our approach. These were used as the base CDSRs for analogical transfers, and can be considered the training data for our evaluation.

>>>>

We evaluated our approach on six classrooms (two simulated and four real) and two simulated studio apartments. The simulated rooms were based on real-life counterparts. For each room we manually encoded the appropriate CDSRs that could be represented by our approach. For the classrooms these were the front and back, and the front and back rows of desk. For the studios these were the kitchen, office and living areas. These manually encoded regions were used as the base CDSRs for analogical transfers, and can be considered the training data for our evaluation.

### 2012-01-23 code/scenarios/cdsr/trunk/papers/AAAI2012/main-aaai12-cdsr.tex
trying to sanitise images and missing bits

\usepackage{float}
\floatstyle{boxed} 
\restylefloat{figure}

@@

Figure \ref{fig:cdsr-reps} contains the symbolic description for the front of classroom \fw{Room1} which is pictured in the top left of Figure~\ref{fig:dora-maps}. The anchor points (connected in green in Figure~\ref{fig:dora-maps}) define the region. \fw{(LeftmostBottomFn Room1)} and \fw{(LeftmostTopFn Room1)} are the points with the lowest x coordinate out of the set of points defined as the top and bottom of \fw{Room1} respectively. The sets of points representing the top and bottom of the classroom are found by selecting the points defining the area within a threshold of the area's maximum or minimum y coordinate. The other corners of the context-dependent spatial region are defined by the four desks and the whiteboard. Because perceived objects (e.g. the desks) are defined as single points, they can serve as anchor points directly. The semantic label \fw{FrontRegion} ties the geometric extent of the boundary points to a conceptual region. This definition for the front of the classroom is specific to \fw{Room1} and its entities. It is clearly context-dependent because its extent is dependent on the arrangement of the anchor points used to define its boundary. If the desks were in a different position then the region would cover a different extent (e.g. if they were closer to the whiteboard then the region would be smaller).

@@

\begin{figure*}[t]
  \includegraphics[width=\textwidth]{images/worked-example.png}
  \caption{\textbf{TODO}}
  \label{fig:rooms-and-pic}
\end{figure*}

\begin{figure}[t]
  \includegraphics[width=\columnwidth]{images/worked-example-rooms.png}
  \caption{\textbf{TODO}}
  \label{fig:rooms}
\end{figure}

\begin{figure}[t]
  \includegraphics[width=\columnwidth]{images/ug40.png}
  \caption{\textbf{TODO}}
  \label{fig:ug40}
\end{figure}

\from{Nick}{I'd like to keep an example like this in the paper, but we need to choose carefully so we can minimise the number of space-consuming images we need}

@@

We first create the base and target representations by running Dora in the two different classrooms \textbf{TODO:image+ref here}. In each case, Dora is manually driven around the room to allow it to create a metric map. Once the map is created, Dora is then positioned such that the objects are observable and the visual recognition system is run. The map and object data that results from this is then passed on to the QSR generator. \from{Nick}{TODO: update for actual example} In the base case, there are 16 desks and a chalkboard. There are two other entities in the case: the room area and the CDSR representing the front of the room. The case includes a total of 96 expressions relating the 19 entities. Nine of these expressions are used to define the boundary of a CDSR representing the front of the room: the four desks in the front row, the chalkboard, and the leftmost bottom and leftmost top of the room. The target case includes only 12 desks arranged in three columns of four, a chalkboard and a lectern. The target case includes 73 statements and 14 entities.

SME generates an analogy between the base and target cases enabling the transfer of the symbolic description of the front of the room to the new situation. The resulting analogy includes 62 correspondences between the entities and expressions in the base and target and 53 candidate inferences.  All seven \fw{regionBoundary} statements in the base appear as candidate inferences. Five of the anchor points are exactly correct, the leftmost corners of the room, the chalkboard and two of the desks in the front row. The other two analogically transferred anchor points are to the lectern and a desk in the third row. Figure \ref{fig:success} illustrates the region created by the seven boundary points in the target environment.

% While this region is not identical to how a human would specify it, our system is able to produce a fairly accurate context-dependent spatial region in a new environment from a single example.

% \begin{figure}[h]
%   \includegraphics[width=\columnwidth]{images/target-success.png}
%   \caption{Successful analogical transfer results in the identification of the front of the room as the green dashed trapezoidal region. The red boxes in rows are the identified desks, the blue box along the wall is the chalkboard, the green box is the lectern, and the green and red object is Dora.}
%   \label{fig:success}
% \end{figure}

>>>>

% \usepackage{float}
% \floatstyle{boxed} 
% \restylefloat{figure}

@@

Figure \ref{fig:cdsr-reps} contains the symbolic description for the front of classroom \fw{Room1} which is pictured in the top of Figure~\ref{fig:rooms}. The anchor points (connected in orange in Figure~\ref{fig:rooms}) define the region. \fw{(LeftmostBottomFn Room1)} and \fw{(LeftmostTopFn Room1)} are the points with the lowest x coordinate out of the set of points defined as the top and bottom of \fw{Room1} respectively. The sets of points representing the top and bottom of the classroom are found by selecting the points defining the area within a threshold of the area's maximum or minimum y coordinate. The other corners of the context-dependent spatial region are defined by the four desks and the whiteboard. Because perceived objects (e.g. the desks) are defined as single points, they can serve as anchor points directly. The semantic label \fw{FrontRegion} ties the geometric extent of the boundary points to a conceptual region. This definition for the front of the classroom is specific to \fw{Room1} and its entities. It is clearly context-dependent because its extent is dependent on the arrangement of the anchor points used to define its boundary. If the desks were in a different position then the region would cover a different extent (e.g. if they were closer to the whiteboard then the region would be smaller).

@@

% all images in a single figure -- pretty ugly and a waste of space
% \begin{figure*}[t]
%   \includegraphics[width=\textwidth]{images/worked-example.png}
%   \caption{\textbf{TODO}}
%   \label{fig:rooms-and-pic}
% \end{figure*}

\begin{figure}
  \includegraphics[width=\columnwidth]{images/worked-example-rooms.png}
  \caption{Maps of 2 real classrooms generated by our system, plus an expert-annotated CDSR (orange, top image), subject-annotated CDSR (red, bottom image) and a CDSR transferred by analogy (green bottom image). The classroom used to generate the top classroom is pictured in Figure~\ref{fig:ug40}}
  \label{fig:rooms}
\end{figure}

\begin{figure}
  \includegraphics[width=\columnwidth]{images/ug40.png}
  \caption{One of the classrooms used in our evaluation. This image was presented to subjects who were  asked to annotate a copy of the image in the bottom half of Figure~\ref{fig:rooms}.}
  \label{fig:ug40}
\end{figure}

@@

We first create the base and target representations by running Dora in the two different classrooms. These are pictured in the top and bottom of Figure~\ref{fig:rooms} respectively. In each case, Dora is manually driven around the room to allow it to create a metric map. Once the map is created, Dora is then positioned such that the objects are observable and the visual recognition system is run. The map and object data that results from this is then passed on to the QSR generator. In the base case Dora perceives 2 desks, a whiteboard and the room area. To this we add the CDSR representing the front of the room. The case includes a total of \textbf{SOMENUMBER} expressions relating the \textbf{SOMENUMBER} entities. \textbf{SOMENUMBER} of these expressions are used to define the boundary of a CDSR representing the front of the room: the \textbf{SOMENUMBER} desks in the front row, the whiteboard, and the leftmost bottom and leftmost top of the room. The target case includes \textbf{SOMENUMBER}. The target case includes \textbf{SOMENUMBER} statements and \textbf{SOMENUMBER} entities.

SME generates an analogy between the base and target cases enabling the transfer of the symbolic description of the front of the room to the new situation. The resulting analogy includes \textbf{SOMENUMBER} correspondences between the entities and expressions in the base and target and \textbf{SOMENUMBER} candidate inferences.  All \textbf{SOMENUMBER} \fw{regionBoundary} statements in the base appear as candidate inferences. \textbf{SOMENUMBER} of the anchor points are exactly correct, the \textbf{\dots}. The other \textbf{SOMENUMBER} analogically transferred anchor points are to the \textbf{\dots}. The green region in the lower image of Figure \ref{fig:rooms} illustrates the CDSR created by the \textbf{SOMENUMBER} boundary points in the target environment.

### 2012-01-23 code/scenarios/cdsr/trunk/papers/AAAI2012/qsr-extraction.tex
JK: qsr-extraction.tex updated (typo correction)
trying to sanitise images and missing bits

\begin{figure}
\centerline{
\includegraphics[width=2in]{./images/spatialRelations/xZeroYOne.png}
}
\caption{A visualisation of a the strength of a spatial relation across a region. In this figure the landmark is located at the center of the image and the direction vector used was $\langle0,1\rangle$ (i.e. above of the landmark). The darker the pixel the stronger the spatial relation is deemed to be at that point.}
\label{fig:spr}
\end{figure}

>>>>

\begin{figure}
\centerline{
\includegraphics[width=\columnwidth]{./images/spatialRelations/xZeroYOne.png}
}
\caption{A visualisation of a the strength of a spatial relation across a region. In this figure the landmark is located at the center of the image and the direction vector used was $\langle0,1\rangle$ (i.e. above of the landmark). The lighter the pixel the stronger the spatial relation is deemed to be at that point.}
\label{fig:spr}
\end{figure}

\from{Nick}{TODO: Generating QSRs is this way allows us to\dots}
